---
title: "RWorksheet_berja#2"
author: "Forge"
date: "2024-09-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1.	Create a vector using : operator
a.	Sequence from -5 to 5. Write the R code and its output. 

Describe its output.

```{r}

seq(-5,5)
```
Using sequence it gave out 11 elements ranging from -5 to 5.

b. x <- 1:7. What will be the value of x?

```{r}
x <- 1:7
x
```
The value of x is 1, 2, 3, 4, 5, 6, 7.


  2. Create a vector using seq() function
  a.	seq(1, 3, by=0.2) # specify step size
  Write the R script and its output. Describe the output.

```{r}
seq(1, 3, by=0.2)
```

The output given was the starting from 1 it adds an indention of 0.2.


  3.	A factory has a census of its workers. There are 50 workers in total. The following list shows their ages:  34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.
 
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
```

a.	Access 3rd element, what is the value?
```{r}
ages[3]
```
The value of the 3rd element is 22.


b.	Access 2nd and 4th element, what are the values?
```{r}
ages[c(2, 4)]
```
The value of the 2nd and the 4th elements is 28, and 36.

\pagebreak
c.	Access all but the 4th and 12th element is not included. Write the R script and its output.
```{r}
ages[-c(4, 12)]
```


4.  *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).    


a.	Print the results. Then access x[c("first", "third")]. Describe the output.

b.	Write the code and its output.
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
names(x)
```
```{r}
x[c("first", "third")]
```
The output given was 3 and 9.

gsub()
5.	Create a sequence x from -3:2.
a.	Modify 2nd element and change it to 0;
x[2] <- 0
x
Describe the output.



b.	Write the code and its output.
```{r}
x <- -3:2
x[2] <- 0
x
```
The output was it sequence from -3 to 2 but at the 2nd element we converted it to 0 instead of 2.

6. *The following data shows the diesel fuel purchased by Mr. Cruz

a.	Create a data frame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.

```{r}
month <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00) 
purchase_quantity <- c(25, 30, 40, 50, 10, 45)


fuel_data <- data.frame(month, price_per_liter, purchase_quantity)


print(fuel_data)
```

\pagebreak

b.	What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use ‘weighted.mean(liter, purchase)‘. Write the R scripts and its output.

```{r}
# a. Creating the data frame
month <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_data <- data.frame(month, price_per_liter, purchase_quantity)

# Display the data frame
print(fuel_data)

# b. Calculating the weighted average fuel expenditure
weighted_avg_expenditure <- weighted.mean(fuel_data$price_per_liter, fuel_data$purchase_quantity)

# Display the result
cat("The average is:", weighted_avg_expenditure, "PhP per liter\n") 
```



7. *R has actually lots of built-in datasets. For example, the rivers data “gives the lengths (in miles) of 141 “major” rivers in North America, as compiled by the US Geological Survey”.
a.	Type “rivers” in your R console.
Create a vector data with 7
elements, containing the number of elements (length) in rivers, their sum (sum), mean (mean), median(median), variance(var), standard deviation(sd), minimum (min) and maximum (max).
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
b.	What are the results?



c.	Write the R scripts and its outputs.

\pagebreak
```{r}
data(rivers)

vector_data <- c(
  length = length(rivers),
  sum = sum(rivers),
  mean = mean(rivers),
  median = median(rivers),
  variance = var(rivers),
  sd = sd(rivers),
  min = min(rivers),
  max = max(rivers)
)


print(vector_data)
```

The results are given its descriptions.


8.	The table below gives the 25 most powerful celebrities and their annual pay as ranked by the editions of Forbes magazine and as listed on the Forbes.com website.



a.	Create vectors according to the above table. Write the R scripts and its output.
```{r}

# a. Create vectors for celebrity names, power rankings, and pay
celebrity_names <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods",
                     "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos",
                     "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali",
                     "Paul McCartney", "George Lucas", "Elton John", "David Letterman",
                     "Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson",
                     "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")

power_ranking <- c(1:13, 14:25)

pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55,
         40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)


celebrity_names
power_ranking
pay

```



b.	Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 and pay to 90. Write the R scripts and its output.
```{r}
power_ranking[power_ranking == 19] <- 15
pay[celebrity_names == "J.K Rowling"] <- 90


celebrity_names
power_ranking
pay
```


c.	Create an excel file from the table above and save it as csv file(PowerRanking). Import the csv file into the RStudio. What is the R script?
\pagebreak
```{r}
PowerRanking <- data.frame(
  PowerRanking = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25),
  CelebrityName = c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods",
"Steven Spielberg", "Howard Stern", "50 Cent","Cast of the Sopranos", "Dan Brown", "Bruce Springsteen",
"Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman",
"Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant"),
  Pay = c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
)


write.csv(PowerRanking, "PowerRanking.csv", row.names = FALSE)


PowerRanking <- read.csv("PowerRanking.csv")


print(PowerRanking)
```

 

d.	Access the rows 10 to 20 and save it as Ranks.RData. Write the R script and its output.
```{r}
power_ranking <- c(1:13, 14:25)
celebrity_name <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2",
                   "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent",
                   "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen",
                   "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas",
                   "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling",
                   "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Lenon",
                   "Celine Dion", "Kobe Bryant")
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34,
         40, 47, 75, 25, 39, 45, 32, 40, 31)
Forbes_Ranking <- data.frame(power_ranking, celebrity_name, pay)
Forbes_Ranking
Ranks <- Forbes_Ranking[10:20, ]
Ranks

save(Ranks, file = "Ranks.RData")
```





e.	Describe its output.
The output is given on the rankings and the payings of each celebrities worldwide.



9.	Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna

\pagebreak
a.	Import the excel file into your RStudio. What is the R script?
```{r}
library(readxl)

hotels_vienna <- read_excel("/cloud/project/R Codes/hotels-vienna.xlsx")
```

The R script is hotels-vienna.xlsx

b.	How many dimensions does the dataset have? What is the R script? WHat is its output?
```{r}
dim(hotels_vienna)
```

c.	Select columns country, neighbourhood, price, stars, accomodation_type, and ratings. Write the R script.
```{r}
library(dplyr)
hotels_vienna_selected <- hotels_vienna %>%
    select(country, neighbourhood, price, stars, accommodation_type, rating )
```



d.	Save the data as **new.RData to your RStudio. Write the R script.
```{r}
save(hotels_vienna_selected, file = "vienna-hotel-repoforge.Rdata")
```

e.	Display the first six rows and last six rows of the new.RData. What is the R script?
```{r}

load("vienna-hotel-repoforge.Rdata")

head(hotels_vienna_selected, 6)

tail(hotels_vienna_selected,6)
```


10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.

a. Write the R scripts and its output.
```{r}
vegetables <- list("Kalabasa", "Kapayas", "Monggo", "Kangkong", "Okra", "Malunggay", "Potatoes", "Ampalaya", "Cabbage", "Asparagus")


vegetables

```

\pagebreak
b. Add 2 additional vegetables after the last vegetables
in the list. What is the R script and its output?

```{r}
vegetables <- c(vegetables, "Tomatoes", "Eggplant")


vegetables
```


\pagebreak
c. Add 4 additional vegetables after index 5. How many
datapoints does your vegetable list have? What is the
R script and its output?

```{r}
vegetables <- c(vegetables[1:5], list("Pechay", "Bawang", "Sitaw", "Singkamas"), vegetables[6:12])

vegetables
```



d. Remove the vegetables in index 5, 10, and 15. How
many vegetables were left? Write the codes and its
output.

```{r}
vegetables <- vegetables[-c(5, 10, 15)]

vegetables
```



 

















