---
title: "RWorksheet_berja#1.Rmd."
author: "Forge"
date: "2024-09-04"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41.

a. How many data points?



-There are 34 data points in total. 



b. Write the R code and its output.


```{r}
    age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
         35, 31, 27, 22, 37, 34, 19, 20, 57, 49,
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51,
         35, 24, 33, 41)
length(age)
```


2. Find the reciprocal of the values for age



Write the R code and its output.
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
         35, 31, 27, 22, 37, 34, 19, 20, 57, 49,
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51,
         35, 24, 33, 41)

reciprocal_age <- 1 / age

print(reciprocal_age)
```


a. How many data points in from 8.1 to 8.4?






3. Assign also new_age <- c(age, 0, age). 
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
         35, 31, 27, 22, 37, 34, 19, 20, 57, 49,
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51,
         35, 24, 33, 41)

new_age <- c(age, 0, age)
```
\pagebreak
What happen to the new_age?



The vectors are concatenated using the c() function to produce the new_age vector, which has 69 components: the first 34 elements from the age vector, one 0 element, and the remaining 34 elements from the age vector that are duplicates.



4. Sort the values for age.



Write the R code and its output.
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
         35, 31, 27, 22, 37, 34, 19, 20, 57, 49,
         50, 37, 46, 25, 17, 37, 42, 53, 41, 51,
         35, 24, 33, 41)

sorted_age <- sort(age)

print(sorted_age)
```



5. Find the minimum and maximum value for age.



Write the R code and its output.
```{r}

min_value <- min(age)

max_value <- max(age)

print(paste("Minimum value:", min_value))
print(paste("Maximum value:", max_value))
```



6. Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, and 2.7.



a. How many data points?



-There are 12 data points in total.



b. Write the R code and its output.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
          2.3, 2.5, 2.3, 2.4, 2.7)

print(data)
```


\pagebreak
7. Generates a new vector for data where you double every value of the data. | What happen to the data?
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
          2.3, 2.5, 2.3, 2.4, 2.7)

doubled_data <- data * 2

print(doubled_data)
```



-The data given to us was doubled because of the codes we inputted into it which makes the given data doubled its output by 2.



8. Generate a sequence for the following scenario:


*8.1 Integers from 1 to 100.
```{r}
sequence_1_to_100 <- seq(from = 1, to = 100)

print(sequence_1_to_100)
```


*8.2 Numbers from 20 to 60 
```{r}
sequence_20_to_60 <- 20:60


print(sequence_20_to_60)
```


*8.3 Mean of numbers from 20 to 60
```{r}
sequence_20_to_60 <- 20:60


mean_value <- mean(sequence_20_to_60)


print(mean_value)
```

\pagebreak
*8.4 Sum of numbers from 51 to 91
```{r}
sequence_51_to_91 <- 51:91


sum_value <- sum(sequence_51_to_91)


print(sum_value)
```


*8.5 Integers from 1 to 1,000
```{r}
sequence_1_to_1000 <- 1:1000


print(sequence_1_to_1000)
```

a. How many data points from 8.1 to 8.4?_______


-There are 143 data points from 8.1 to 8.4.


b. Write the R code and its output from 8.1 to 8.4.


8.1
```{r}
sequence_1_to_100 <- seq(from = 1, to = 100)

print(sequence_1_to_100)
```

\pagebreak
8.2
```{r}
sequence_20_to_60 <- 20:60


print(sequence_20_to_60)
```


8.3
```{r}
sequence_20_to_60 <- 20:60


mean_value <- mean(sequence_20_to_60)


print(mean_value)
```


8.4
```{r}
sequence_51_to_91 <- 51:91


sum_value <- sum(sequence_51_to_91)


print(sum_value)
```


c. For 8.5 find only maximum data points until 10.
```{r}
sequence_1_to_1000 <- 1:1000

limit <- 10

filtered_sequence <- sequence_1_to_1000[sequence_1_to_1000 <= limit]

print(filtered_sequence)

```


9. *Print a vector with the integers between 1 and 100 that are not divisible by 3, 5 and 7 using filter option.


Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))


Write the R code and its output
```{r}
sequence_1_to_100 <- seq(100)

filtered_sequence <- Filter(function(i) { all(i %% c(3, 5, 7) != 0) }, sequence_1_to_100)

print(filtered_sequence)

```


10. Generate a sequence backwards of the integers from 1 to 100.


Write the R code and its output
```{r}
sequence_1_to_100 <- 1:100

reversed_sequence <- rev(sequence_1_to_100)

print(reversed_sequence)

```


11. List all the natural numbers below 25 that are multiples of 3 or 5.


Find the sum of these multipliers
```{r}

numbers_below_25 <- 1:24


multiples_of_3_or_5 <- numbers_below_25[numbers_below_25 %% 3 == 0 | numbers_below_25 %% 5 == 0]


sum_of_multiples <- sum(multiples_of_3_or_5)


print(multiples_of_3_or_5)
print(sum_of_multiples)
```




a. How many data points from 10 to 11?


-There are 112 data points from 10 to 11.


b. Write the R code and its output from 10 and 11.


10.
```{r}
sequence_1_to_100 <- 1:100

reversed_sequence <- rev(sequence_1_to_100)

print(reversed_sequence)
```

\pagebreak
11.
```{r}

numbers_below_25 <- 1:24


multiples_of_3_or_5 <- numbers_below_25[numbers_below_25 %% 3 == 0 | numbers_below_25 %% 5 == 0]


sum_of_multiples <- sum(multiples_of_3_or_5)


print(multiples_of_3_or_5)
print(sum_of_multiples)
```


12. Statements can be grouped together using braces ‘{’ and ‘}’. A group of statements is sometimes called a block. Single statements are evaluated when a new line is typed at the end of the syntactically complete statement. Blocks are not evaluated until a new line is entered after the closing brace.


Enter this statement:


x <- {0 + x + 5 + }


Describe the output.

#Error: unexpected '}' in "x <- {0 + x + 5 +"

The trailing + in the original expression x <- {0 + x + 5 + } causes a syntax error. The problem can be fixed and the phrase can be evaluated correctly by taking out the + and making sure it is complete.


13. *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75, 75 and 77. To access individual elements of an atomic vector, one generally uses the x[i] construction.

Find x[2] and x[3]. Write the R code and its output.

```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
score[2]
score[3]
```


*Create a vector a = c(1,2,NA,4,NA,6,7).
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
```


a. Change the NA to 999 using the codes print(a,na.print="-999").


```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)


print(a, na.print="-999")
```

\pagebreak
b. Write the R code and its output. Describe the output.
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)


print(a, na.print="-999")
```


The vector an is shown with NA values rendered as -999 for display purposes using the print(a, na.print="-999") command this approach might be helpful for reporting or visualization.


15. A special type of function calls can appear on the left hand side of the assignment operator as in > class(x) <- "foo".


Follow the codes below:


name = readline(prompt="Input your name: ")


age = readline(prompt="Input your age: ")


print(paste("My name is",name, "and I am",age ,"years old."))


print(R.version.string)


What is the output of the above code?
```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is", name, "and I am", age, "years old."))
print(R.version.string)
```





