---
title: "RWorksheet_berja#4a"
author: "Forge"
date: "2024-10-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.

a. Describe the data.

```{r}
household <- data.frame(
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)

print(household)
```

\pagebreak

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.

```{r}
males <- household[household$Gender == "M",]
females <- household[household$Gender == "F",]

print(males)
print(females)
```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
mean(household$Shoe_size)
mean(household$Height)
```

d. Is there a relationship between shoe size and height? Why?

Yes
```{r}
cor(household$Shoe_size, household$Height)
```

\pagebreak

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.

```{r}
months <- c("March", "April", "January", "November", "January", 
            "September", "October", "September", "November", 
            "August", "January", "November", "November", 
            "February", "May", "August", "July", 
            "December", "August", "August", "September", 
            "November", "February", "April")

factor_months_vector <- factor(months)

print(factor_months_vector)

levels(factor_months_vector)
```

3. Then check the summary() of the months_vector and factor_months_vector. | Interpret the results of both vectors. Are they both equally useful in this case?
```{r}

```




